---
title: "Assignment 5"
author: "Juliette Verstaen"
date: "6/5/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Here’s what the package should contain

1. at least two different functions that summarize climate data in some way (your choice - it could be finding a trend, or finding extremes; or even simply mean winter precipitation)

Grapes take three years to grow 
- cant get too cold 
- needs lots 

functions:
1. maximum (and minimum) temperature for each year -> gives you table (use an array here maybe one array is temp min and one array is max ; month and year will be the row and column labels)
2. graph precipitation 
3. calculate index scores: if temperature reaches below X then returns a "temp too low for growing"; if temp reaerches above X then return "temp high, water more") -> different for red vs white grapes
4.  Do a regression that temp and precp has on grapes harvested?
5. Regression for rain and temeprature on price (one function that estimates the costs of impacts)
(this could be the array: one array with the climate data, year seperated out, and another array matching the years with the total harvested and price this could be a third array for price each year)

4. some sample data
5. documentation for ALL functions
6. a vignette that shows how to use several of the functions with the sample data
7. 3 separate tests - (next weeks lecture)

```{r}
library(tidyverse)
```


Units:
weight of grapes = thousand tons
price = $/ton
Temp = F
Precipitation = cm

Read in Data
```{r}

#need to figure out how to source this data witho
napaclimraw <- read_csv("data/napaclim_raw.csv")

clim <- napaclimraw %>%
  select(DATE, TMIN, TMAX, TAVG, PRCP)

grapes <- read_csv("data/grape_crushed.csv")%>%
  select(Year, napa_red_ttons, napa_white_ttons, red_price, white_price)

```


Data Tidying
```{r}

#climate data
names(clim) <- c("year", "tmin", "tmax", "tavg", "precip")
clim <- clim %>%
  separate(year, c("year", "month"), by = "-") 
#a few years have no data so omit them cause 0s would skew data
clim <- na.omit(clim)

#write.csv(clim, "clim.csv")

names(grapes) <- c("date", "red_weight", "white_weight", "red_price", "white_price")
#write.csv(grapes, "grapes.csv")


```

Clear everything and load in the new data frames so everything is nice and clean from now on

```{r}

clim <- read_csv("data/clim.csv")
grapes <- read_csv("data/grapes.csv")

```


Functions:

1. Maximum (and minimum) temperature for each year -> gives you table (use an array here maybe one array is temp min and one array is max ; month and year will be the row and column labels)
```{r}

temp_array <- array(dim= c(23,12,2))
dim(temp_array)
temp_array

```



2. Graph total yearly precipitation 
```{r}

#data = clim when actually using it
graph_precip = function(data = clim) {
  
  func2 <- clim %>%
    group_by(year) %>%
    summarize(annual_precip = sum(precip))%>%
    ungroup()
  
  graph <- ggplot(func2) +
  geom_line(aes(x=year, y= annual_precip, group = 1), color= "navy") +
    ggtitle("Annual Total Precipitation") +
    xlab("Year") +
    ylab("Precipitation (cm)")+
    theme_classic()+
    theme(axis.text.x=element_text(angle=90, hjust=1))
  
  return(graph)
  
}
```

3. Calculate index scores: if temperature reaches below X then returns a "temp too low for growing"; if temp reaerches above X then return "temp high, water more")
Pretend: 
- both = 4
- below 38F = 3
- above 82 = 2
- anything else = 1

Here assuming that colder is worse, grapes can withstand hotter temps better as long as watered, but harder to protect agaisnt cold
```{r}

temp_threshold = function(clim) {
 
test <-  mutate(clim, 
    index = case_when(
    tmin < "38" ~ "3",
    tmax > "82" ~ "2", 
    tmin < "38"  & tmax > "82" ~ "4"))
 #   tmin >= "38"  & tmax <= "82" ~ "1")
  test  
    
    
    
    
  ))
  
}


  
  


```



















