---
title: "Assignment 5"
author: "Juliette Verstaen"
date: "6/5/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Questions for Casey:
- estimation of costs of impacts: do you have to run the impact function first and use those outputs as an input for the cost function or should it be integrated into the fucntion?
- regression in 3.5 is giving me a table but also a weird error "length of NULL cannot be changedlength of NULL cannot be changedlength of NULL cannot be changedlength of NULL cannot be changedlength of NULL cannot be changed"
- should we source the function in the tests?



Here’s what the package should contain

functions:
1. maximum (and minimum) temperature for each year -> gives you table (use an array here maybe one array is temp min and one array is max ; month and year will be the row and column labels)
2. graph precipitation 
3. calculate index scores: if temperature reaches below X then returns a "temp too low for growing"; if temp reaerches above X then return "temp high, water more") -> different for red vs white grapes
4.  Do a regression that temp and precp has on grapes harvested?
5. Regression for rain and temeprature on price (one function that estimates the costs of impacts)
(this could be the array: one array with the climate data, year seperated out, and another array matching the years with the total harvested and price this could be a third array for price each year)

4. some sample data
5. documentation for ALL functions
6. a vignette that shows how to use several of the functions with the sample data
7. 3 separate tests - (next weeks lecture)


Notes:
- functions need to be robust enought to take additional data from other places
```{r}
library(tidyverse)

library(tidyverse)
library(gapminder)
library(lmtest)
library(sandwich)
library(broom)
library(stargazer)
library(knitr)
library(car)

```


Units:
weight of grapes = thousand tons
price = $/ton
Temp = F
Precipitation = cm

Read in Data
```{r}

#need to figure out how to source this data witho
napaclimraw <- read_csv("data/napaclim_raw.csv")

clim <- napaclimraw %>%
  select(DATE, TMIN, TMAX, TAVG, PRCP)

grapes <- read_csv("data/grape_crushed.csv")%>%
  select(Year, napa_red_ttons, napa_white_ttons, red_price, white_price)

```


Data Tidying
```{r}

#climate data
names(clim) <- c("year", "tmin", "tmax", "tavg", "precip")
clim <- clim %>%
  separate(year, c("year", "month"), by = "-") 
#a few years have no data so omit them cause 0s would skew data
clim <- na.omit(clim)

write.csv(clim, "clim.csv")

names(grapes) <- c("year", "red_weight", "white_weight", "red_price", "white_price")
write.csv(grapes, "grapes.csv")


```

Clear everything and load in the new data frames so everything is nice and clean from now on

```{r}

clim <- read_csv("data/clim.csv")
grapes <- read_csv("data/grapes.csv")

```


Functions:

1. Maximum (and minimum) temperature for each year -> gives you table (use an array here maybe one array is temp min and one array is max ; month and year will be the row and column labels)
```{r}

temp_array <- array(dim= c(23,12,2))
dim(temp_array)
temp_array

```



2. Graph total yearly precipitation 
```{r}

#data = clim when actually using it
graph_precip = function(clim) {
  
  func2 <- clim %>%
    group_by(year) %>%
    summarize(annual_precip = sum(precip))%>%
    ungroup()
  
  min_precip <- min(func2$annual_precip)
  
  max_precip <- max(func2$annual_precip)
  
  graph_precip<- ggplot(func2) +
  geom_line(aes(x=year, y= annual_precip, group = 1), color= "navy") +
    ggtitle("Annual Total Precipitation") +
    xlab("Year") +
    ylab("Precipitation (cm)")+
    theme_classic()+
    theme(axis.text.x=element_text(angle=90, hjust=1))
  
  return(list(graph_precip, min_precip=min_precip, max_precip=max_precip))
  
}

graph_precip(clim)

```


3. Calculate index scores: if temperature reaches below X then returns a "temp too low for growing"; if temp reaerches above X then return "temp high, water more")
Pretend: 
- both = 4
- below 38F = 3
- above 82 = 2
- anything else = 1

Here assuming that colder is worse, grapes can withstand hotter temps better as long as watered, but harder to protect agaisnt cold

option to choose precipitation and do the same thing with precip levels
```{r}

temp_threshold = function(clim, weather ) {
  
  if( weather == "temperature") {

  clim$index = ifelse(clim$tmin < 38  & clim$tmax > 82, 4,
                       ifelse(clim$tmin <= 38, 3, 
                          ifelse( clim$tmax >= 82, 2, 
                                  1)))
  #summarize months out of each year where the temperature was outside of the thresholds
  
  out_thresh <- clim %>%
    group_by(year) %>%
    count(index = index)
  
   out_thresh$index <- as.factor(out_thresh$index) 
  
  graph_threshold <- ggplot(out_thresh) +
    geom_histogram(aes(x= year, y= n, fill=index), stat = "identity") +
    theme_classic() +
    labs(title = "Number of months at each index per year ", caption = "*Years with missing data do not have 12 months") +
    xlab("Year") +
    ylab("Number Months *") +
    scale_fill_brewer(palette="Spectral") }
  
  if(weather == "precipitation") {
    clim$index = ifelse(clim$precip <= 1, 3, 
                          ifelse( clim$precip >= 10, 2, 
                                  1))
  #summarize months out of each year where the temperature was outside of the thresholds
  
  out_thresh <- clim %>%
    group_by(year) %>%
    count(index = index)
  
   out_thresh$index <- as.factor(out_thresh$index) 
  
  graph_threshold <- ggplot(out_thresh) +
    geom_histogram(aes(x= year, y= n, fill=index), stat = "identity") +
    theme_classic() +
    labs(title = "Number of months at each index per year ", caption = "*Years with missing data do not have 12 months") +
    xlab("Year") +
    ylab("Number Months *") +
    scale_fill_brewer(palette="PuBu") }
    
  
  return(graph_threshold)
  
}

```

3.5. Regression: effcts temp and precip has on grapes harvest (total, red, white)

```{r}

effect_clim_harvest = function(clim, grapes) {
  
  library(stargazer)
  
  clim_grape <- left_join(clim, grapes, by = "year")
  
  clim_grape <- clim_grape %>%
    mutate(average_weight = (red_price+white_price)/2) 
  
  ##regressions for climate effects on price
  lm_redharv <- lm(red_weight ~ precip + tavg, data = clim_grape)
  lm_whiteharv <- lm(white_weight ~ precip + tavg, data = clim_grape)
  lm_totalharv <- lm(average_weight ~ precip + tavg, data = clim_grape)

stargazer(lm_redharv, lm_whiteharv, lm_totalharv, type="text", title="Regression Results: Effects of Climate on Grape Harvest", dep.var.labels=c("Red", "White", "Avg Both" ), align=TRUE)
  
}

  
```


4. Regression graphs predicting price from harvest
### figure out how to choose the color and change the legend titlt
```{r}
 
effect_harv_price = function(clim, grapes) {
  
  clim_grape <- left_join(clim, grapes, by = "year")
  
  clim_grape <- clim_grape %>%
    mutate(total_weight=red_weight+white_weight) %>%
    mutate(average_price = (red_price+white_price)/2) 
  
  ##regressions for amount harvested on price
  lm_redharv <- lm(red_price ~ red_weight, data = clim_grape)
  summary(lm_redharv)
  
  lm_whiteharv <- lm(average_price ~ white_weight, data = clim_grape)
  summary(lm_whiteharv)
    
  lm_totalharv <- lm(average_price ~ total_weight, data = clim_grape)
  summary(lm_totalharv)
  
  graph_harv_price <- ggplot(clim_grape) +
    geom_point(aes(x= red_weight, y= red_price), color = "red4")+
    stat_smooth(aes(x= red_weight, y= red_price, color= "Red Grapes"),method = "lm", fill = "red4")+

    geom_point(aes(x= white_weight, y= white_price), color= "yellow4")+
    stat_smooth(aes(x= white_weight, y= white_price, color = "White Grapes"),method = "lm", fill= "yellow4")+
    geom_point(aes(x= total_weight, y= average_price))+
    stat_smooth(aes(x= total_weight, y= average_price, color = "Both Grapes"),method = "lm", fill = "gray4")+
    scale_colour_manual(values = c("Both Grapes" = "gray4", "Red Grapes" = "red4", "White Grapes" = "yellow4"))+
    xlab("Weight (thousand tons)")+
    ylab("Price ($/ton)") +
    theme_classic() +
    ggtitle("Effects of Harvest on Price")
  
    graph_harv_price
  
  return(graph_harv_price)
  
}
  
```



5. Regression that temp and precp has on grapes price (total, red, white)
- estimating the costs of impacts

```{r}

effect_index_price = function(clim, grapes) {
  
  library(stargazer)
  
  clim$index_temp = ifelse(clim$tmin < 38  & clim$tmax > 82, 4,
                       ifelse(clim$tmin <= 38, 3, 
                          ifelse( clim$tmax >= 82, 2, 
                                  1)))
  
   clim$index_precip = ifelse(clim$precip <= 1, 3, 
                          ifelse( clim$precip >= 10, 2, 
                                  1))

  
   clim$index_precip <- as.factor(clim$index_precip) 
      clim$index_temp <- as.factor(clim$index_temp) 
  
  clim_grape <- left_join(clim, grapes, by = "year")
  
  clim_grape <- clim_grape %>%
    mutate(total_weight=red_weight+white_weight) %>%
    mutate(average_price = (red_price+white_price)/2) 
  
  ##regressions for climate effects on price
  lm_redprice <- lm(red_price ~ index_precip + index_temp, data = clim_grape)
  lm_whiteprice <- lm(white_price ~ index_precip + index_temp, data = clim_grape)
  lm_totalprice <- lm(average_price ~ index_precip + index_temp, data = clim_grape)

stargazer(lm_redprice, lm_whiteprice, lm_totalprice, type="text", title="Regression Results: Effects of Climate Indices on Grape Price", dep.var.labels=c("Red", "White", "Avg Both" ), align=TRUE)
  
}
  
```

###Testing
```{r error = TRUE}

library(devtools)
library(testthat)

#source function to test?

##Test 1
test_that("graph_precip", { 
  clim_test_data =
  as.data.frame(
    cbind(
      year  = c(1995:2018),
      precip  = runif(min=0, max=50, n=24),
      tavg = runif(min=30, max= 95, n=24)
    )
  )
  expect_true(graph_precip(clim_test_data)$min_precip>=0)
  expect_true(graph_precip(clim_test_data)$max_precip>=0)})

##Test 2
test_that()
grape_test_data =
  as.data.fram(
    cbind(
      year  = c(1995:2018),
      red_weight = runif(min= 40, max= 100, n=24),
      red_weight = runif(min= 400, max= 730, n=24),
      red_price = runif(min= 100, max= 1000, n=24),
      white_price = runif(min= 350, max= 650, n=24)
    )
  )


expect_true()


##Test 3
## expect that for function temp_threshold() there wont be any indexes in a year that equals more than 12


```










