---
title: "Assignment_1"
author: "Juliette Verstaen"
date: "5/2/2019"
output: pdf_document
toc: true
toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##A. Import and Tidy

```{r}

###load packages
library(tidyverse)

###set working directory to Assignment_1 folder
getwd()

###load in raw data
parcels_raw <- 
  read_csv("data/Santa_Barbara_County_parcels_2011.csv")
 ### tried col_types because Frew said to in class, but then I couldn't calculate anything later so I hashed tagged it out
#                        col_types = cols(.default = col_character())) %>%
  as_tibble()

###select only columns of interest
parcels <-
  transmute(parcels_raw,
    APN       = APN,
    Situs1    = Situs1,
    Situs2    = Situs2,
    Acreage   = Acreage,
    UseCode   = UseCode,
    NonTaxCode= NonTaxCode,
    AgPres    = AgPres,
    LandValue = LandValue,
    Net_Impr  = Net_Impr,
    Net_AV    = Net_AV,
    M_Address1 = M_Address1,
    M_Address2 = M_Address2)

###Convert all blanks in tibble to NAs    
parcels[is.na(parcels)] <- "NA"

###write to CSV file
parcels <- write_delim(parcels,
  "parcels.csv",
  delim = "|",
  na = ""
)

parcels
```

##B. Analyze

###1. What are the 10 most-frequently-occuring land uses (in descending order)? 
```{r}

###load in use code data
use_code <- read_delim("data/UseCodes.csv", 
                       delim="|", 
                       quote= "")
                    #   col_types = cols(.default = col_character()))
use_code[is.na(use_code)] <- "NA"

###combine the parcels data with the use code data
parcels_codes <- left_join(parcels, use_code, by="UseCode")

###count the most 10 most frequenctly occuring land uses
top_10 <- parcels_codes %>%
  count(UseCode) %>%
  arrange(desc(n)) %>%
  head(10) 

###add the code descriptions to the top 10 counted so you know what they are
B1_topfreq <-  left_join(top_10, use_code, by="UseCode") %>%
  select("UseCode", "n", "CodeDesc")

```

###2. How many acres are in agricultural preserves?

```{r}

###choose only parcels that are agricultural preserves and have acreage values
agpres <- parcels_codes %>%
  filter(AgPres != "NA") %>%
  filter(Acreage != "NA") 

###add up the number of acres in an ag preserve
B2_agpres <- sum(agpres$Acreage)
B2_agpres

```

###3. What is the mean net assessed value per acre of the entire county?
add up cost of all peices and then divide by the area

```{r}

###pick out acreage and net average value of the parcels
### remove any of the parcels that are less than or equal to 0, with the assumption that is incorrect/unknown data
mean_county <- parcels_codes %>%
  select("Acreage", "Net_AV") %>%
  filter(Net_AV >=0)

###make vectors of sum of average value and sum of acreage
sum_av <- sum(mean_county$Net_AV)
sum_ac <- sum(mean_county$Acreage)

###math for average price/acre
B3_meannv <- sum_av/sum_ac
B3_meannv

```

###4. What is the total net assessed value of all non-taxable parcels?

```{r}

###keep only parcels that are non-taxable
mean_nontax <- parcels_codes%>%
  filter(NonTaxCode != "NA")

###Find the total net assessed value
B4_totalnontax <- sum(mean_nontax$Net_AV)

B4_totalnontax

```


###5. What are the 10 largest property holders, by acreage? 

```{r}

###Keep only properties that have full mailing addresses and keep top 10 acreage wise
B5_topacre <- parcels_codes%>%
  filter(M_Address1 != "NA") %>%
  filter(M_Address2 != "NA") %>%
  unite(address, c("M_Address1", "M_Address2"), sep = " ") %>%
  arrange(desc(Acreage)) %>%
  head(10)%>%
  select("address", "Net_AV", "Acreage")

B5_topacre

###how did san fransisco make it into the SB county data??

```

###6. What are the 10 largest property holders, by net assessed value?

```{r}

###Keep only properties that have full mailing addresses and keep top 10 net assessed value wise
B6_topnv <- parcels_codes%>%
  filter(M_Address1 != "NA") %>%
  filter(M_Address2 != "NA") %>%
  unite(address, c("M_Address1", "M_Address2"), sep = " ") %>%
  arrange(desc(Net_AV)) %>%
  head(10) %>%
  select("address", "Net_AV", "Acreage")

B6_topnv

```
