---
title: "Notes"
author: "Juliette Verstaen"
date: "4/19/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

https://r4ds.had.co.nz/introduction.html
```{r}
#install.packages(c("nycflights13", "gapminder", "Lahman"))

library(nycflights13)
library(gapminder)
library(Lahman)
library(tidyverse)

```

A tibble = constraint on a dataframe. type of data frame that doesn't have real identifyiers, doesn't conform text into factors
- subset of a dataframe, makes t easier for all your data loaded in to be more consistant

```{r}
as_tibble(iris)
```


the <> is the type 
- dbl = double precision number
- fct = factor

Can build a tibble out of formulas
```{r}
tibble(
  x= 1:5, 
  y= 1,
  z= x^2+y
)


df <- tibble(
  x = runif(5),
  y = rnorm(5)
)

df %>% .$x



```

```{r}

heights <- read_csv("r4ds/heights.csv")

```

```{r}
charToRaw("Hadley")


```

can use select function and rename at the same time
example:
select( df, 
id= FEATUREID, lat= PRIM_LAT_DEC)

if have data that is filler and not real (ie: 0 for lat long can make them NAs)
ex: gaz$lat = parse_double(gaz$lat, na= "0")

########
5/3/2019

Tiddy
```{r}

library(tidyverse)

setwd()

gaz_raw <- 
  read_delim("gazetter.zip",
             delim = "|",
             col_types = cols(.default = col_character())
             )

gaz_raw

#can select, rename, and apply transformations
gaz <- 
  transmute(gaz_raw,
            id = parse_integer(FEATURE_ID),
            name = FEATURE_NAME,
            class = FEATURE_CLASS,
            state = STATE_ALPHA,
            county = COUNTY_NAME,
            lat = parse_double(PRIM_LAT_DEC, na= "0"),
            lon = parse_double(PRIM_LONG_DEC, na ="0"),
            map = parse_character(MAP_NAME, na= "Unknown"),
            created_on = parese_date(DATE_EDited, format = "%m/%d/%Y" ))


gaz <- filter(gaz,
              !is.na(lon) &
                !is.na(lat)&
                state == "CA")


wrote <- write_delim(gaz,
                     "gaxetteer.csv",
                     delim = "|",
                     na= "" # saying that all Nas are just empty space, standard way to do this is csv file
                     )
```

Analyze

1. most-frequntly occuring feature name
gaz %>% 
count(name) %>%
filter (n == max(n))


2. least frequently occuring feature class?
gaz %>%
count(class) %>%
filter(n == min(n))

3. What is the approximate center point of each county?
- this creates a box that fits all the points and then identifying the center. issues: most of the points could be skewed to one side

gaz %>%
filter(!is.na(county)) %>%
group_by(county) %>%
summarize(
ctr_lo = (min(lon) + max(lon)) /2,
ctr_lat = (min(lat) + max(lat)) /2) %>%
ungroup()
)

4. what are the fractions of the total numver of features in each county that are natural? man-made?
a. create a tibble with 2 columns: feature class and feature category("natural", "man-made", or NA if we can't tell). Add 1 row for each unique feature class

categories <- tribble(
~class, ~category,
"Airport", "manmade",
"Arch", "natural",
"Area", "natural",
"Arroyo", "natural"
"Bar", " natural",
""

)

All of this stuff and more is in the gazetter.rmd file


Chapter 13
```{r}

```















