---
title: "Week3"
author: "Juliette Verstaen"
date: "4/19/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

https://r4ds.had.co.nz/introduction.html
```{r}
#install.packages(c("nycflights13", "gapminder", "Lahman"))

library(nycflights13)
library(gapminder)
library(Lahman)
library(tidyverse)

```

A tibble = constraint on a dataframe. type of data frame that doesn't have real identifyiers, doesn't conform text into factors
- subset of a dataframe, makes t easier for all your data loaded in to be more consistant

```{r}
as_tibble(iris)
```


the <> is the type 
- dbl = double precision number
- fct = factor

Can build a tibble out of formulas
```{r}
tibble(
  x= 1:5, 
  y= 1,
  z= x^2+y
)


df <- tibble(
  x = runif(5),
  y = rnorm(5)
)

df %>% .$x



```

```{r}

heights <- read_csv("r4ds/heights.csv")

```

```{r}
charToRaw("Hadley")


```

can use select function and rename at the same time
example:
select( df, 
id= FEATUREID, lat= PRIM_LAT_DEC)

if have data that is filler and not real (ie: 0 for lat long can make them NAs)
ex: gaz$lat = parse_double(gaz$lat, na= "0")




