---
title: "Assignment_2"
author: "Juliette Verstaen"
date: "5/2/2019"
output: pdf_document
toc: true
toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##A. Import and Tidy

SB county parcels data
```{r}
###load packages
library(tidyverse)

###set working directory to Assignment_1 folder
getwd()

###load in raw data
parcels_raw <- 
  read_csv("data/Santa_Barbara_County_parcels_2011.csv", 
            col_types = cols(.default = col_character())) %>%
  as_tibble()

###select only columns of interest
parcels <-
  transmute(parcels_raw,
    APN       = APN,
    Situs1    = Situs1,
    Situs2    = Situs2,
    Acreage   = parse_double(Acreage, na = "0"),
    UseCode   = UseCode,
    NonTaxCode= NonTaxCode,
    AgPres    = AgPres,
    LandValue = parse_double(LandValue, na = "0"),
    Net_Impr  = parse_double(Net_Impr, na = "0"),
    Net_AV    = parse_double(Net_AV, na = "0"),
    M_Address1 = M_Address1,
    M_Address2 = M_Address2)

###Convert all blanks in tibble to NAs    
parcels[is.na(parcels)] <- NA
```

Use code data
```{r}
###load in use code data
use_code <- read_delim("data/UseCodes.csv", 
                       delim="|", 
                       quote= "", 
                       col_types = cols(.default = col_character()))

use_code[is.na(use_code)] <- NA
```


Creating a connection to SQLite and a parcels database
```{r}
library(DBI)
  ###establish connection
db <- dbConnect(RSQLite::SQLite(), 
                dbname = "parcels.db")

  ###add in parcels data table
dbWriteTable(conn = db, name = "parcels", value = parcels, overwrite = TRUE)

  ###add in use code data table
dbWriteTable(conn = db, name = "use_code", value = use_code, overwrite = TRUE)

  ### arguments within the dbWriteTable()
  ### the first argument is the connection handle;

  ### the second is the name for the table inside the database; 

  ### the third is the dataframe with all your beautifully processed data.

dbListTables(db) ### double checking that tables are there. YAY it works

```

##B. Analyze the data using SQL

###1.What are the 10 most-frequently-occuring land uses (in descending order)?
```{sql connection=db}

SELECT CodeDesc, COUNT(CodeDesc) AS Appearances
FROM  parcels JOIN use_code 
ON    parcels.UseCode = use_code.UseCode
GROUP BY CodeDesc  
ORDER BY Appearances DESC
LIMIT 10;

```

###2. How many acres are in agricultural preserves?
```{sql connection=db}

SELECT sum(Acreage)
FROM   parcels JOIN use_code
ON     parcels.UseCode = use_code.UseCode
WHERE AgPres IS NOT NULL;

```

###3. What is the mean net assessed value per acre of the entire county?

```{sql connection=db}

SELECT round(sum(Net_AV)/sum(Acreage), 2)
FROM   parcels JOIN use_code
ON     parcels.UseCode = use_code.UseCode
WHERE Net_AV >=0;

```

###4. What is the total net assessed value of all non-taxable parcels?
   Assume non-taxable parcels are indicated by non-NA values for NonTaxCode.
```{sql connection=db}

SELECT sum(Net_AV)
FROM   parcels JOIN use_code
ON     parcels.UseCode = use_code.UseCode
WHERE  NonTaxCode IS NOT NULL AND Net_AV >=0 ;

```

###5. What are the 10 largest property holders, by acreage?

```{sql connection=db}

SELECT parcels.M_Address1, parcels.M_Address2, sum(Acreage)
FROM   parcels JOIN use_code
ON     parcels.UseCode = use_code.UseCode
WHERE M_Address1 IS NOT NULL OR M_Address2 IS NOT NULL
GROUP BY parcels.M_Address1, parcels.M_Address2
Order By sum(Acreage) DESC
LIMIT 10;

```

###6. What are the 10 largest property holders, by net assessed value?
```{sql connection=db}

SELECT parcels.M_Address1, parcels.M_Address2, sum(Net_AV)
FROM   parcels JOIN use_code
ON     parcels.UseCode = use_code.UseCode
WHERE M_Address1 IS NOT NULL OR M_Address2 IS NOT NULL
GROUP BY parcels.M_Address1, parcels.M_Address2
Order By sum(Net_AV) DESC
LIMIT 10;

```

Close the sql database connection
```{r}
dbDisconnect(db)
```









