---
title: "Assignment_4"
author: "Juliette Verstaen"
date: "5/28/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Write a function that takes as input

a table that has prices for different fish a table that has the number caught for each fish species for each location * each location is in a different column * each fish is in a different row

Function output will be

    most frequently caught fish in each location
    total revenue for each location

    total fisheries revenue sum

    if user requests it graph of revenue by location and total revenue (as text)

Place your function in an *.R file Make a package that contains this function

Generate some example data for your function; and show how this is created and used in an R markdown document Submit package and Rmarkdown as usual as a git link on gauchospace


```{r}
library(tidyverse)
library(dplyr)
```

### Create test data
```{r}

### create vector of possible fish 
possible.fish = c("parrotfish","unicornfish","bonito","yellowfin","swordfish")

###Fish Catch Data
### number of fish caught on northside
catch_north <- sample(possible.fish, size=20, replace=T) %>%
  as_tibble %>%
  group_by(value) %>%
  count()

colnames(catch_north) <- c("fish", "north")

### number of fish caught on eastside
catch_east <- sample(possible.fish, size=20, replace=T) %>%
  as_tibble %>%
  group_by(value) %>%
  count()

colnames(catch_east) <- c("fish", "east")

### number of fish caught on westside
catch_west <- sample(possible.fish, size=20, replace=T) %>%
  as_tibble %>%
  group_by(value) %>%
  count()

colnames(catch_west) <- c("fish", "west")

### combine all together

catch_all_1 <- left_join(catch_north, catch_east, by= "fish")
catch_location_data <- left_join(catch_all_1, catch_west, by= "fish")


### Price Data

price_data <- c("4000","15000", "20000", "25000", "20000") %>%
  as_tibble()

colnames(price_data) <- c("price") 
rownames(price_data) <- c("parrot", "unicorn", "bonito", "yellowfin","swordfish")


# because possible.fish was a factor catch1 will be a factor

summary(catch_location_data)
# if we want summary to be more useful - make this a factor
catch_north = as.factor(catch_location_data)

# to quickly get frequencies of different fish and to plot 
summary(catch_location_data)
plot(catch_location_data$north, col="blue")

```





